%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\usepackage{afterpage}
\usepackage{hyperref}
\usepackage{color}
\usepackage{xcolor}
%\usepackage{fontawesome}
\hypersetup{
    pdftitle={},
    pdfauthor={},
    pdfsubject={},
    pdfkeywords={},
    colorlinks=false,       % no lik border color
   allbordercolors=white    % white border color for all
}
\RequirePackage{xcolor}
\definecolor{pblue}{HTML}{0395DE}

\usepackage{enumitem}

\begin{document}
\header{Victor M.}{Mendiola-Lau}{Software Engineer and Consultant}

% Fake text to add separator      
\fcolorbox{white}{gray}{\parbox{\dimexpr\textwidth-2\fboxsep-2\fboxrule}{%
.....
}}

% In the aside, each new line forces a line break
\begin{aside}
  \section{Contact}
  	~
    Miami, FL, USA
    (+1) 786-630-0166
    \href{mailto:ryuzakyl@gmail.com}{\textbf{ryuzakyl@}gmail.com}
    ~
    ~
    ~
  \section{Online profiles}
  	~
    \href{https://ryuzakyl.github.io}{{\scriptsize ryuzakyl.github.io}}
    \href{https://github.com/ryuzakyl}{{\scriptsize github.com/ryuzakyl}}
    \href{https://www.linkedin.com/in/victormendiolalau}{{\scriptsize linkedin.com/in/VictorMendiolaLau}}
%	\href{https://www.researchgate.net/profile/Victor_Mendiola-Lau}{{\scriptsize researchgate.net/Victor\char`_Mendiola-Lau}}
    ~
    ~
    ~
  \section{Personal skills}
    ~
	\smartdiagram[bubble diagram]{
        \textbf{Curiosity},
        \textbf{Team Work},
        \textbf{Initiative},
        \textbf{Responsibility},
        \textbf{Dedicated}
    }
	~
	~
	~
  \section{About me}
    ~
    I'm a Software Engineer with a taste for creativity, both in code and the kitchen. I usually enjoy sports and exploring any kind of outdoor activities. When I'm not coding, I love to spend time with friends and family.
\end{aside}

\section{Work Experience}
\begin{entrylist}
  \entry
    {2022 - 2023}
    {DevOps Engineer}
    {Rolla Finance, USA}
    {My main responsibilities include the definition and implementation of our Cloud, Kubernetes, Monitoring and Security infrastructure.\\}

  \entry
    {2020 - 2021}
    {Cybersecurity Intern}
    {EY, Málaga, Spain}
    {As part of the Pentesting team I worked on generating security compliance reports with CIS Benchmark guides.\\}

  \entry
    {}
    {Senior Fullstack Web Developer}
    {Novoshore, Málaga, Spain}
    {Wide range of responsibilities in Swiss Fintech Startup client. Frontend Technologies: Angular. Backend Technologies: NodeJS, Spring Boot, Java, PostgreSQL.\\}

  \entry
    {2019 - 2020}
    {Fullstack Web Developer}
    {Ottawa, Canada} % {Iversoft - Digital consultancy & technology partner. (https://www.iversoft.ca/)}
    {Construction of an organization's website. Technologies: Wordpress, PHP, HTML, CSS3, JavaScript, MySQL, etc.\\} 

  \entry
    {2018 - 2019}
    {Software Engineer}
    {Kitsune Technologies, Tennessee, USA}
    {Wide range of responsibilities including Data Analysis, Computer Vision, Web development, services implementation, etc.\\}

  \entry
    {}
    {Python/Flask Backend Engineer}
    {Freelance, Cuba} %{Ezequiel}
    {Used Selenium and ChromeDriver combined with Celery/Redis to develop a REST API simulating user behavior to bypass CAPTCHA-based security.\\}  

  \entry
    {2017 - 2018}
    {Fullstack Web Developer}
    {Ottawa, Canada} % {HRSG - Human Resource Systems Group Ltd. (https://www.hrsg.ca/)}
    {Web-based applications as solutions to workforce management. Technologies: PHP, HTML, CSS3, JavaScript, jQuery, MySQL, etc.\\} 

  \entry
    {}
    {Python/Django Backend Engineer}
    {SBY Technologies, Florida, USA}
    {Developed a REST API from the ground up with JWT Authentication, automatic reports generation (.pdf, .csv), etc. Also worked as a DevOps Engineer and Linux System Administrator.\\}    

  \entry
    {2016}
    {Ruby/Rails Backend Engineer}
    {Ksabes, Havana, Cuba}
    {Completely engineered and developed an API relying on Json Web Token (JWT) for authentication.\\}
  
  \entry
    {2014 - 2015}
    {Ruby Developer}
    {IRStrat, México D.F., México}
    {Completely engineered and developed a multi-threaded and concurrent service for consuming real time stock market data.\\}
    
  \entry
    {2013 - 2017}
    {Data Science and Machine Learning Engineer}
    {CENATAV, Havana, Cuba}
    {Used Data Science and Machine Learning to design and implement Pattern Recognition systems using C\#/C++. Also worked as a Software Engineer designing and implementing efficient algorithms.\\}
\end{entrylist}

\section{Education/Academic background}
\begin{entrylist}
  \entry
    {2019 - 2021}
    {Master's Degree in Cyber Security}
    {University of Jaén, Spain}
    {
    	Main subjects: Secure Cloud Applications, Network Security, Intrusion Detection, Reverse Engineering, Malware Analysis, Advanced Cryptography.\\
      Thesis: \emph{``Study and implementation of security controls for Kubernetes clusters''.}\\
    }

  \entry
    {2008 - 2013}
    {B.Sc. in Computer Science}
    {University of Havana, Cuba}
    {B.Sc. in Computer Science (5.13 of 5.0).\\ Main subjects: Programming, Algorithms and Data Structures, Computational Complexity Theory, Matematics, Operational Research, Numerical Matematics and Artificial Intelligence.\\
    Thesis: \emph{``Iris Recognition using Functional Data Analysis (FDA)''.}}

%  \entry
%    {2004 - 2007}
%    {Bachelor Diploma}
%    {IPVCE Vladimir Ilich Lenin, Havana, Cuba}
%    {Bachelor diploma with focus on these subjects: Matematics and Computer Science.}
\end{entrylist}

\section{Languages}
\begin{entrylist}
  \entry
    {\textbf{Spanish}}
    {}
    {}
    {Native tongue}      

  \entry
    {\textbf{English}}
    {}
    {}
    {
    	\textbf{Proficient user}: IELTS score 7.0 overall (corresponding to \textbf{C1} in CEFR). 
    	Graduated \textbf{\emph{summa cum laude}} at \emph{Abraham Lincoln} Languages School.\\
    }

  \entry
    {\textbf{French}}
    {}
    {}
    {Diplôme d'études en langue française (\textbf{DELF B2}) à l'Alliance française.}
\end{entrylist}

\section{Research \& Teaching}
\begin{entrylist}
  \entry
    {2017 - 2018}
    {Visiting Researcher}
    {University of Seville, Spain}
    {Researcher in topics like Machine Learning and Data Analysis.\\}

  \entry
    {}
    {Instructor Professor}
    {University of Havana, Cuba}
    {Math instructor of topics such as Set theory, Functions, Algebra, Calculus, Numerical math and Ordinary Differential Equations.\\}

  \entry
    {2013 - 2017}
    {Researcher}
    {CENATAV, Havana, Cuba}
    {Design and development of Pattern Recognition Systems. Junior researcher and PhD. student. Interest on topics like Machine Learning, Data Analysis, Data Representation and Computer Vision. Technologies: Python, Numpy, SciPy, Matplotlib, scikit-learn, etc.\\}

  \entry
    {2012}
    {Research internship}
    {CENATAV, Havana, Cuba}
    {Design and implementation of an iris encoding method based on Functional Data Analysis (FDA).\\}
    
  \entry
    {2010 - 2013}
    {Assistant Instructor}
    {University of Havana, Cuba}
    {Instructor of Programming and Algorithms for Mathematics students in the Faculty of Mathematics and Computer Science (MATCOM).\\}
\end{entrylist}

% \pagebreak

% \section{Technologies}
% \begin{entrylist}
%   \entry
%     {\textbf{Languages}}
%     {}
%     {}
%     {\textbf{C\#} (+9 years), \textbf{Python} (+7 years), \textbf{C/C++} (+5 years), \textbf{Ruby} (+2 years), \textbf{PHP} (+2 years). Other languages include \textbf{Go} and \textbf{Java}.}

%   \entry
%     {\textbf{IDEs\&Editors}}
%     {}
%     {}
%     {\textbf{Visual Studio}, \textbf{VS Code} and \textbf{JetBrains IDEs}.}
  
%   \entry
%     {\textbf{ML \& DA}}
%     {}
%     {}
%     {The Python stack for Machine Learning and Data Analysis: \textbf{Numpy}, \textbf{SciPy}, \textbf{Pandas}, \textbf{scikit-learn} and \textbf{Matplotlib}. Also the \textbf{MATLAB} programming language and environment.}

%   \entry
%     {\textbf{Web}}
%     {}
%     {}
%     {\textbf{HTML}, \textbf{CSS3}, \textbf{JavaScript}, \textbf{Vue.js}, \textbf{jQuery}, \textbf{PHP}, \textbf{Django}, \textbf{Django Rest Framework}, \textbf{ASP.NET MVC/Core} and \textbf{Ruby on Rails}.}
    
%   \entry
%     {\textbf{Cloud}}
%     {}
%     {}
%     {\textbf{AWS} and \textbf{Google Cloud Platform}.}

%   \entry
%     {\textbf{Desktop}}
%     {}
%     {}
%     {\textbf{.NET}, \textbf{.NET Core} and \textbf{Qt}.}
% \end{entrylist}

% \begin{entrylist}
%   \entry
%     {\textbf{DVCS}}
%     {}
%     {}
%     {\textbf{Git} (+5 years) (\textbf{GitHub}, \textbf{GitLab} and \textbf{Bitbucket}).}
    
%   \entry
%     {\textbf{DBMS}}
%     {}
%     {}
%     {\textbf{PostgreSQL}, \textbf{Microsoft SQL Server}, \textbf{MySQL} and \textbf{SQLite}.}
    
%   \entry
%     {\textbf{CV}}
%     {}
%     {}
%     {\textbf{OpenCV}, \textbf{EmguCV} and \textbf{OpenCV-Python bindings}.}      
    
%   \entry
%     {\textbf{OS}}
%     {}
%     {}
%     {\textbf{GNU/Linux} (+4 years) (\textbf{Ubuntu}, \textbf{Linux Mint}) y \textbf{Microsoft Windows} (+12 years).}
% \end{entrylist}
% \\
% \section{Other Accomplishments}
% \begin{itemize}[noitemsep, nolistsep]

% 	\item Achieved a GPA of 5.13 over a scale of 5.0\footnote{The extra points were the result of outstanding academic achievements.}.\\

% 	\item ACM-ICPC Cuban Finals contestant (2011 and 2013 editions)\footnote{Competed for a spot in ACM-ICPC Caribbean Finals contest.}.\\

% 	\item Winner of the $1^{st}$ prize at the 2010-2011 Scientific Journal of the Faculty of Mathematics and Computer Science.\\
	
% 	\item I have made some contributions to the Wikipedia article entitled ``\emph{Computational complexity theory}".\\
		
% 	\item Winner of the silver medal in Mathematics of the $12^{ve}$ grade in Havana.\\
	
% 	% \item From 2004 until 2007 was selected as part of advanced groups in Mathematics.\\	
	
% 	% \item Best candidate\footnote{Highest grade.} of the \emph{Plaza de la Revolución} locality at the IPVCE Vladimir Ilich Lenin admission tests in 2003-2004.\\	
	
% 	% \item Valedictorian from my elementary school in 2001.\\	
	
% \end{itemize}

\end{document}
