%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Victor M. Mendiola Lau} \\ \vspace{1pt}
    Miami, FL \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ (+1) 786 630 0166 ~ \href{mailto:ryuzakyl@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ryuzakyl@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/victormendiolalau}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/victormendiolalau}}  ~
    \href{https://github.com/ryuzakyl}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/ryuzakyl}}
    \vspace{-8pt}
\end{center}

Senior Full Stack Engineer with over 10 years of experience designing robust and scalable backend systems and APIs, with a strong focus
on cloud infrastructure automation and DevOps practices.

%
%-----------PROGRAMMING SKILLS-----------

\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Programming}{: C\# (10 years), Python (8 years), C++ (4 years), Java (2 years), Golang (1 year), Git, GitHub, Linux.} \\
      \textbf{Web}{: HTML5, CSS3, Javascript, ASP.NET MVC/Core, Django/DRF, WordPress.} \\
      \textbf{Machine Learning/AI \& Data Analysis}{: LangChain, Numpy, SciPy, Pandas, scikit-learn, Matplotlib, OpenCV.} \\
      \textbf{Cloud \& DevOps}{: Docker, Kubernetes, Terraform, Redis, Kafka, AWS, Azure.} \\
      \textbf{Databases}{: SQL, MS SQL Server, PostgreSQL, MySQL.} \\
      \textbf{Languages}{: Spanish (native), English (native), French (intermediate).} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------EXPERIENCE-----------

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {LaceUp Solutions, Inc.}{May 2023 -- Present}
      {Senior Software Engineer}{Miami, FL}
      \resumeItemListStart
        \resumeItem{Optimized a .NET DevExpress desktop app data-intensive operations with efficient algorithms, boosting query performances by 10x in some cases.}
        \resumeItem{Leveraged LLMs and LangChain to create a PoC AI-powered assistant to "chat" with business data, improving operational efficiency and the decision-making processes.}
        \resumeItem{Configured and deployed a resilient data layer with Azure SQL Database, achieving 99.99\% availability SLA and enhancing data integrity.}
        \resumeItem{Designed and maintained GitHub workflows, completely eliminating deployment errors and shortening release cycles to roughly $\sim$30\% of the initial time.}
      \resumeItemListEnd
      \begin{itemize}[leftmargin=0.0in, label={}]
        \small{
          \item{
            \emph{Technologies}{: .NET, C\#, SQL, Entity Framework, DevExpress, MS SQL Server, Python, AI, Azure.} \\
          }
        }
      \end{itemize}

    \resumeSubheading
      {Stealth Crypto Startup (DeFi)}{May 2021 -- February 2023}
      {Senior Software/DevOps Engineer (Remote)}{Málaga, Spain}
      \resumeItemListStart
        \resumeItem{Configured and optimized our AWS cloud resources using Terraform and Kubernetes, leading to reduced provisioning time and a production grade cloud infrastructure.}
        \resumeItem{Setup OAuth2 authentication for our public API documentation and other security related configurations (TLS, GeoIP blocking, rate limiting, etc.).}
        \resumeItem{Integrated Prometheus and Grafana for enhanced observability, and optimized resource allocation, reducing infrastructure costs by $\sim$33\%.}
        \resumeItem{Designed and implemented load/stress testing protocols, enabling the system to horizontally scale and handle increased traffic.}
      \resumeItemListEnd
      \begin{itemize}[leftmargin=0.0in, label={}]
        \small{
          \item{
            \emph{Technologies}{: AWS, K8s, Docker, Python, Terraform, PostgreSQL, Apache Kafka, Redis, Prometheus, Grafana.} \\
          }
        }
      \end{itemize}


    \resumeSubheading
      {Novoshore}{May 2020 -- April 2021}
      {Senior Fullstack Web Developer}{Málaga, Spain}
      \resumeItemListStart
        \resumeItem{Delivered features that met 100\% of stringent financial industry standards and regulatory requirements for a Swiss Fintech startup, ensuring compliance and security.}
        \resumeItem{Developed and containerized Spring Boot backend microservices, enhancing deployment efficiency and decreasing server response time by $\sim$12\%.}
    \resumeItemListEnd
    \begin{itemize}[leftmargin=0.0in, label={}]
      \small{
        \item{
          \emph{Technologies}{: .Node.js, Javascript, Spring Boot, Java, Angular, MongoDB, PostgreSQL, Docker.} \\
        }
      }
    \end{itemize}

    \resumeSubheading
      {Kitsune Technologies}{June 2018 -- April 2020}
      {Senior Software Engineer (Remote)}{}
      \resumeItemListStart
        \resumeItem{Developed and deployed ML models for Speech Segmentation and Computer Vision, reaching close to $\sim$90\% accuracy.}
        \resumeItem{Architected and implemented scalable API and microservices infrastructure to support our web applications.}
        \resumeItem{Part of cross-discipline teams to design/validate ML models, increasing end customer relevant metrics by $\sim$18\% overall.}
      \resumeItemListEnd
    \begin{itemize}[leftmargin=0.0in, label={}]
      \small{
        \item{
          \emph{Technologies}{: Python, numpy, pandas, OpenCV, Flask, Vue.js, C\#, etc.} \\
        }
      }
    \end{itemize}

    \resumeSubheading
      {Freelance}{2016 -- 2018}
      {Fullstack Web Developer (Remote) $|$ \emph{Wordpress, PHP, HTML, CSS3, JavaScript, MySQL, etc.}}{}
      \resumeItemListStart
        \resumeItem{Worked in the ground-up development of a FIFA member organization's official website.}
        \resumeItem{Drove the development of key features, including responsive design, content management integration, and performance optimization.}
      \resumeItemListEnd

      {Fullstack Web Developer (Remote) $|$ \emph{PHP, HTML, CSS3, JavaScript, jQuery, SQL, MySQL, etc.}}{}
      \vspace{-8pt}
      \resumeItemListStart
        \resumeItem{Developed and implemented many features in a web-based workforce management solution using a proprietary PHP framework.}
        \resumeItem{Built a robust backend foundation by crafting efficient SQL queries and optimizing database structures, ensuring optimal application performance and long-term maintainability.}
      \resumeItemListEnd

    \resumeSubheading
      {Project-Based Freelance}{2014 -- 2016}
      {Python Backend Engineer (Remote) $|$ \emph{Python, Flask, Celery, Redis}}{}
      \resumeItemListStart
        \resumeItem{Used Selenium and ChromeDriver combined with Celery and Redis to develop a REST API simulating user behavior to bypass CAPTCHA-based security.}
      \resumeItemListEnd

      {Python Backend Engineer (Remote) $|$ \emph{Python, Django, DRF, JWT Authentication}}{}
      \vspace{-8pt}
      \resumeItemListStart
        \resumeItem{Developed a REST API from the ground up with JWT Authentication, automatic reports generation (.pdf, .csv), etc.}
      \resumeItemListEnd

      {Ruby Backend Engineer (Remote) $|$ \emph{Ruby, Ruby on Rails}}{}
      \vspace{-8pt}
      \resumeItemListStart
        \resumeItem{Completely engineered and developed an API relying on Json Web Token (JWT) for authentication.}
      \resumeItemListEnd

      {Ruby Backend Engineer (Remote) $|$ \emph{Ruby}}{}
      \vspace{-8pt}
      \resumeItemListStart
        \resumeItem{Completely engineered and developed a multi-threaded and concurrent service for consuming real time stock market data.}
      \resumeItemListEnd

      \resumeSubheading
      {CENATAV}{September 2013 -- August 2017}
      {Data Science and Machine Learning Engineer}{Havana, Cuba}
      \resumeItemListStart
        \resumeItem{Designed, tested and successfully implemented real-world Pattern Recognition solutions, achieving precisions $>$95\%.}
        \resumeItem{Leveraged data science and machine learning expertise to develop innovative pattern recognition solutions that were used in real world applications.}
        \resumeItem{Accelerated research to production workflows by designing an internal toolkit for testing and validating classification and clustering strategies, reducing research time by roughly $\sim$25\%.}
      \resumeItemListEnd
    \begin{itemize}[leftmargin=0.0in, label={}]
      \small{
        \item{
          \emph{Technologies}{: .NET, C\#, C++, Python, numpy, Pandas, scikit-learn, OpenCV, MATLAB, etc.} \\
        }
      }
    \end{itemize}

  \resumeSubHeadingListEnd

  \vspace{-16pt}

%-----------EDUCATION-----------

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Jaén}{2019 -- 2021}
      {M.Sc. in Cybersecurity}{Jaén, Spain}
      \begin{itemize}[leftmargin=0.0in, label={}]
        \small{
          \item{
            \emph{Thesis}{: Study and implementation of security controls for Kubernetes clusters} \\
          }
        }
     \end{itemize}
    \resumeSubheading
      {University of Havana}{2008 -- 2013}
      {B.Sc. in Computer Science (Summa cum laude)(GPA: 5.13/5.0)}{Havana, Cuba}
      \begin{itemize}[leftmargin=0.0in, label={}]
        \small{
          \item{
            \emph{Thesis}{: Iris Recognition using Functional Data Analysis (FDA)} \\
          }
        }
     \end{itemize}
  \resumeSubHeadingListEnd


%------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Data Structures
%                 \item Software Methodology
%                 \item Algorithms Analysis
%                 \item Database Management
%                 \item Artificial Intelligence
%                 \item Internet Technology
%                 \item Systems Programming
%                 \item Computer Architecture
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     %\resumeSubHeadingListEnd

%-----------INVOLVEMENT---------------

\section{Research \& Teaching}
    \resumeSubHeadingListStart

      \resumeSubheading{University of Seville}{2018}{Visiting Researcher}{Seville, Spain}
          \resumeItemListStart
              \resumeItem{Conducted research and developed computer vision algorithms for human silhouette detection, object tracking, etc.}
          \resumeItemListEnd

          \resumeSubheading{University of Havana}{2017 -- 2018}{Instructor Professor}{Havana, Cuba}
          \resumeItemListStart
              \resumeItem{Math instructor of topics such as Set theory, Functions, Algebra, Calculus, Numerical math and Ordinary Differential Equations.}
          \resumeItemListEnd

          \resumeSubheading{CENATAV}{2013 -- 2017}{Researcher}{Havana, Cuba}
          \resumeItemListStart
              \resumeItem{Design and development of Pattern Recognition Systems. Junior researcher and PhD. student. Interest on topics like Machine Learning, Data Analysis, Data Representation and Computer Vision.}
          \resumeItemListEnd

          % \resumeSubheading{CENATAV}{2012}{Research internship}{Havana, Cuba}
          % \resumeItemListStart
          %     \resumeItem{Design and implementation of an iris encoding method based on Functional Data Analysis (FDA).}
          % \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------

% \section{Other Projects}
%     \vspace{-5pt}
%     \resumeSubHeadingListStart
%         \resumeProjectHeading
%           {\textbf{twitter-language-detection} $|$ \emph{Python, Matplotlib}}{2018}
%           \resumeItemListStart
%             \resumeItem{Developed an implementation for language detection in tweets using traditional NLP techniques and visualization for data analysis.}
%           \resumeItemListEnd

%           \vspace{-13pt}

%         \resumeProjectHeading
%           {\textbf{data-bloodhound} $|$ \emph{Python, numpy, scikit-learn, C++}}{2017}
%           \resumeItemListStart
%             \resumeItem{Developed a toolbox for data analysis with the aim of ease validation and implementation of Pattern Recognition and Big Data solutions.}
%           \resumeItemListEnd

%           \vspace{-13pt}

%         \resumeProjectHeading
%           {\textbf{yapir (Yet Another Platform for Iris Recognition)} $|$ \emph{Python, numpy, scikit-learn, Qt}}{2013}
%           \resumeItemListStart
%             \resumeItem{Created a platform/application allowing to perform basic Iris Recognition tasks using FDA-based algorithms.}
%           \resumeItemListEnd

%     \resumeSubHeadingListEnd
% \vspace{-15pt}

\end{document}
